### 2014-01-02 thesis/src/chapters/chapter-7-evaluation.tex
Add configuration of csap/carina/one in terms of information manager and policy evaluation interval

Because \emph{Carina} is capable of only horizontal scaling and \emph{Cloud-SAP} of both horizontal and vertical, one can question whether the descent in CPU usage can be actually the same in both cases. To answer this question we want to look into the description of the virtual machines comprising the deployed environment. It states that each VM can use up to 30\% power of the CPU of a host. Thus, we can be fairly sure that adding another virtual machine that uses 0.3 CPU capacity of its host is equivalent with changing the CPU usage settings of already deployed VM from 30 to 60\%.
\subsection*{Preconditions}
\subsubsection*{Environment specification}
\begin{asparaenum}
  \item[\textbf{Deployment diagrams}] Deployment diagrams show the placement of each component in both installations. They are shown in figures \ref{eval:auto-scaling-1cp-carina-deployment-diagram} and \ref{eval:auto-scaling-1cp-cloud-sap-deployment-diagram}.

@@

  \begin{figure}[!ht]
    \begin{center}
      \includegraphics{chapter-7/cpu-usage-cloud-sap-deployment-diagram}
    \end{center}
    \caption{Auto-scaling - single-provider based: deployment diagram of Cloud-SAP}
    \label{eval:auto-scaling-1cp-cloud-sap-deployment-diagram}
  \end{figure}
\item[\textbf{Auto-scaling policy specifications}] As it is shown in figure \ref{eval:auto-scaling-1cp-cpu-usage-function}, we set in both products the threshold values of CPU usage that trigger performing auto-scaling actions to 20 and 60 percent. To apply this setting, the auto-scaling part of service specification looks as follows: in Carina \ldots \ldots ; in Cloud-SAP it is a matter of setting appropriate arguments to a specific policy. In this case the policy is \emph{threshold\_model} and values are 20 and 60 for lower and upper bound respectively. The auto-scaling part from service specification is shown in listing \ref{lst:auto-scaling-1cp-cloud-sap-service-spec}.
  \lstinputlisting[caption=Cloud-SAP service specification used for testing auto-scaling with 1 cloud provider, label=lst:auto-scaling-1cp-cloud-sap-service-spec]{auto-scaling-1cp-cloud-sap-service-spec}
\end{asparaenum}

\subsubsection*{Hardware VM configuration}
All virtual machines were deployed onto \emph{Node1}, which uses \emph{OpenVZ} as a virtualization technology and whose hardware configuration can be found in table \ref{tbl:test-deployment-time-common-hardware-configuration}. \emph{OpenNebula} was installed on a \emph{Frontend1} virtual machine and its configuration is in the same table. \emph{Carina} required the usage of 2 virtual machines which were deployed on \emph{Desktop} with KVM as a hypervisor and whose configuration is in table \ref{tbl:test-auto-scaling-1cp-hardware-configuration}. Diagram \ref{eval:auto-scaling-1cp-physical-nodes} illustrates the physical setup of the test-case.

>>>>

Because \emph{Carina} is capable of only horizontal scaling and \emph{Cloud-SAP} of both horizontal and vertical, one can question whether the descent in CPU usage can be actually the same in both cases. To answer this question we want to look into the description of the virtual machines comprising the deployed environment. It states that each VM can use up to 30\% power of the CPU of a host. Thus, we can be fairly sure that adding another virtual machine that uses 0.3 CPU capacity of its host is equivalent with changing the CPU usage settings of already deployed VM from 30 to 60\%.
\subsection*{Preconditions}
\subsubsection*{Environment specification}
\begin{asparaenum}
  \item[\textbf{Auto-scaling policy specifications}] As it is shown in figure \ref{eval:auto-scaling-1cp-cpu-usage-function}, we set in both products the threshold values of CPU usage that trigger performing auto-scaling actions to 20 and 60 percent. To apply this setting, the auto-scaling part of service specification looks as follows: in Carina the user has to add the parameters of an auto-scaling policy in a hash that describes the environment under key \emph{:elasticy\_policy}. It is possible to specify the minimal and the maximal number of virtual machines that forms the environment and, what is most important, expressions which evaluation results in scaling the application. The part responsible for this is shown in listing \ref{lst:auto-scaling-1cp-carina-service-spec}.\lstinputlisting[caption=Carina service specification used for testing auto-scaling with 1 cloud provider, label=lst:auto-scaling-1cp-carina-service-spec]{auto-scaling-1cp-carina-service-spec} In Cloud-SAP it is a matter of setting appropriate arguments to a specific policy. In this case the policy is \emph{threshold\_model} and values are 20 and 60 for lower and upper bound respectively. The auto-scaling part from service specification is shown in listing \ref{lst:auto-scaling-1cp-cloud-sap-service-spec}. \lstinputlisting[caption=Cloud-SAP service specification used for testing auto-scaling with 1 cloud provider, label=lst:auto-scaling-1cp-cloud-sap-service-spec]{auto-scaling-1cp-cloud-sap-service-spec}
  \item[\textbf{OpenNebulaa/Carina/Cloud-SAP configuration}] Since Carina and Cloud-SAP used two different instances of OpenNebula installed on separate virtual machines, it is essential the configuration be the same on each of them. Listing \ref{lst:auto-scaling-1cp-one-config} shows the most important OpenNebula excerpt from settings file used in this test case -- polling interval specification, which was set to 30 seconds. To ensure that both products can actually use up-to-date data, they should evaluate their policies every 30 seconds or longer. In Carina the user cannot specify this value, because it is hard-coded in source code to 60 seconds. In Cloud-SAP, however, this value was set in a configuration file and was equal to 60 seconds as well as in Carina. \lstinputlisting[caption=OpenNebula configuration excerpt -- information manager, label=lst:auto-scaling-1cp-one-config]{auto-scaling-1cp-one-config}
  \item[\textbf{Deployment diagrams}] Deployment diagrams show the placement of each component in both installations. They are shown in figures \ref{eval:auto-scaling-1cp-carina-deployment-diagram} and \ref{eval:auto-scaling-1cp-cloud-sap-deployment-diagram}.

@@

  \begin{figure}[!ht]
    \begin{center}
      \includegraphics{chapter-7/cpu-usage-cloud-sap-deployment-diagram}
    \end{center}
    \caption{Auto-scaling - single-provider based: deployment diagram of Cloud-SAP}
    \label{eval:auto-scaling-1cp-cloud-sap-deployment-diagram}
  \end{figure}

  \end{asparaenum}

\subsubsection*{Hardware/VM configuration}
All virtual machines were deployed onto \emph{Node1}, which uses \emph{OpenVZ} as a virtualization technology and whose hardware configuration can be found in table \ref{tbl:test-deployment-time-common-hardware-configuration}. \emph{OpenNebula} was installed on a \emph{Frontend1} virtual machine and its configuration is in the same table. \emph{Carina} required the usage of 2 virtual machines which were deployed on \emph{Desktop} with KVM as a hypervisor and whose configuration is in table \ref{tbl:test-auto-scaling-1cp-hardware-configuration}. Diagram \ref{eval:auto-scaling-1cp-physical-nodes} illustrates the physical setup of the test-case.
